Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-09-24 write_up/F_changes.tex
JJP updates

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Tue Sep 17 17:32:36 2019
\begin{longtable}{rlrrrllr}
\caption{Fishing mortality effects of the
	     closure scenarios (ordered by most effective first)} \\ 
  \hline
Scenario No & Population & F before & F after & \% F change & data type & timescale & resolution \\ 
  \hline
  9 & Population 3 & 1.08 & 0.29 & -73.47 & True Population & weekly & 1.00 \\ 
   10 & Population 3 & 1.08 & 0.29 & -72.94 & True Population & monthly & 1.00 \\ 
   11 & Population 3 & 1.08 & 0.35 & -68.04 & True Population & yearly & 1.00 \\ 
   45 & Population 3 & 1.08 & 0.58 & -46.70 & commercial & yearly & 20.00 \\ 
    1 & Population 3 & 1.08 & 0.58 & -46.21 & commercial & weekly & 1.00 \\ 
   23 & Population 3 & 1.08 & 0.59 & -45.27 & True Population & weekly & 5.00 \\ 
    2 & Population 3 & 1.08 & 0.59 & -45.06 & commercial & monthly & 1.00 \\ 
    7 & Population 3 & 1.08 & 0.60 & -44.48 & survey & yearly & 1.00 \\ 
   24 & Population 3 & 1.08 & 0.61 & -43.20 & True Population & monthly & 5.00 \\ 
    3 & Population 3 & 1.08 & 0.64 & -40.82 & commercial & yearly & 1.00 \\ 
   25 & Population 3 & 1.08 & 0.65 & -39.94 & True Population & yearly & 5.00 \\ 
   17 & Population 3 & 1.08 & 0.67 & -38.11 & commercial & yearly & 5.00 \\ 
   15 & Population 3 & 1.08 & 0.71 & -34.38 & commercial & weekly & 5.00 \\ 
   43 & Population 3 & 1.08 & 0.71 & -34.31 & commercial & weekly & 20.00 \\ 
   16 & Population 3 & 1.08 & 0.73 & -32.58 & commercial & monthly & 5.00 \\ 
   51 & Population 3 & 1.08 & 0.78 & -27.92 & True Population & weekly & 20.00 \\ 
   37 & Population 3 & 1.08 & 0.78 & -27.76 & True Population & weekly & 10.00 \\ 
   39 & Population 3 & 1.08 & 0.79 & -26.98 & True Population & yearly & 10.00 \\ 
   38 & Population 3 & 1.08 & 0.81 & -25.47 & True Population & monthly & 10.00 \\ 
   21 & Population 3 & 1.08 & 0.81 & -25.21 & survey & yearly & 5.00 \\ 
   35 & Population 3 & 1.08 & 0.81 & -25.05 & survey & yearly & 10.00 \\ 
   44 & Population 3 & 1.08 & 0.87 & -19.91 & commercial & monthly & 20.00 \\ 
   52 & Population 3 & 1.08 & 0.88 & -18.39 & True Population & monthly & 20.00 \\ 
   30 & Population 3 & 1.08 & 0.96 & -11.06 & commercial & monthly & 10.00 \\ 
   29 & Population 3 & 1.08 & 0.98 & -9.80 & commercial & weekly & 10.00 \\ 
   31 & Population 3 & 1.08 & 1.03 & -4.36 & commercial & yearly & 10.00 \\ 
   53 & Population 3 & 1.08 & 1.06 & -1.64 & True Population & yearly & 20.00 \\ 
   49 & Population 3 & 1.08 & 1.07 & -1.01 & survey & yearly & 20.00 \\ 
   \hline
\hline
\label{tab:6}
\end{longtable}

>>>>

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Tue Sep 24 20:53:17 2019
\begin{longtable}{rrrllr}
\caption{Fishing mortality effects of the
     closure scenarios on population 3 (ordered by most effective
first). The fishing mortality
     rate before the closure was 1.08.} \\ 
  \hline
Scenario No & F after closure & \% F change & data type & timescale & resolution \\ 
  \hline
  9 & 0.29 & -73.47 & true Population & weekly & 1.00 \\ 
   10 & 0.29 & -72.94 & true Population & monthly & 1.00 \\ 
   11 & 0.35 & -68.04 & true Population & yearly & 1.00 \\ 
   45 & 0.58 & -46.70 & commercial & yearly & 20.00 \\ 
    1 & 0.58 & -46.21 & commercial & weekly & 1.00 \\ 
   23 & 0.59 & -45.27 & true Population & weekly & 5.00 \\ 
    2 & 0.59 & -45.06 & commercial & monthly & 1.00 \\ 
    7 & 0.60 & -44.48 & survey & yearly & 1.00 \\ 
   24 & 0.61 & -43.20 & true Population & monthly & 5.00 \\ 
    3 & 0.64 & -40.82 & commercial & yearly & 1.00 \\ 
   25 & 0.65 & -39.94 & true Population & yearly & 5.00 \\ 
   17 & 0.67 & -38.11 & commercial & yearly & 5.00 \\ 
   15 & 0.71 & -34.38 & commercial & weekly & 5.00 \\ 
   43 & 0.71 & -34.31 & commercial & weekly & 20.00 \\ 
   16 & 0.73 & -32.58 & commercial & monthly & 5.00 \\ 
   51 & 0.78 & -27.92 & true Population & weekly & 20.00 \\ 
   37 & 0.78 & -27.76 & true Population & weekly & 10.00 \\ 
   39 & 0.79 & -26.98 & true Population & yearly & 10.00 \\ 
   38 & 0.81 & -25.47 & true Population & monthly & 10.00 \\ 
   21 & 0.81 & -25.21 & survey & yearly & 5.00 \\ 
   35 & 0.81 & -25.05 & survey & yearly & 10.00 \\ 
   44 & 0.87 & -19.91 & commercial & monthly & 20.00 \\ 
   52 & 0.88 & -18.39 & true Population & monthly & 20.00 \\ 
   30 & 0.96 & -11.06 & commercial & monthly & 10.00 \\ 
   29 & 0.98 & -9.80 & commercial & weekly & 10.00 \\ 
   31 & 1.03 & -4.36 & commercial & yearly & 10.00 \\ 
   53 & 1.06 & -1.64 & true Population & yearly & 20.00 \\ 
   49 & 1.07 & -1.01 & survey & yearly & 20.00 \\ 
   \hline
\hline
\label{tab:6}
\end{longtable}

### 2019-09-24 write_up/mixfishsim_ecolmod.tex
JJP updates

To simulate fish population distribution in space and time a Gaussian spatial
process was employed to model habitat suitability for each of the populations
on a 2d grid.  We first defined a Gaussian random field process, $\{S(c) : c \in
\mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the joint
distribution of $S = \{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian with a
\textit{Matérn} covariance structure, where the correlation strength weakens
with distance. This enables us to model the spatial autocorrelation observed in
animal populations where density is more similar in nearby locations
\citep{Tobler1970, F.Dormann2007, Poos2007} and we change the parameters to
implement different spatial structures for the different populations using the
\textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
habitat field and combine it with a temporally dynamic thermal tolerance field to
imitate two key drivers of population dynamics. Each population was initialised
at a single location, and subsequently moved across the entire space according
to a probabilistic distribution based on habitat suitability (represented by
the normalised values
from the GRFs), temperature and distance from current cell: 
\begin{equation}
	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda \cdot d_{I,J}} \cdot
		(Hab_{J,p}^2 \cdot
		Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}\mathrm{e}^{-\lambda \cdot d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}
Where $d_{I,J}$ is the euclidean distance between cell $I$ and cell $J$,
$\lambda$ is a given rate of decay, $Hab_{c,p}^2$ is the squared index of
habitat suitability for cell $c$ and population $p$, with $Tol_{c,p,wk}$ the
temperature tolerance for cell $c$ by population $p$ in week $wk$ (see
below). \\

@@

Several studies \citep[for a review]{Girardin2016} have confirmed past activity
and past catch rates are strong predictors of fishing location choice. For this
reason, the fleet dynamics sub-model included a learning component, where a
vessel's initial fishing location in a trip was based on selecting from
previously successful fishing locations. This was achieved by calculating an
expected revenue based on the catches from locations fished in the preceding
trip as well as the same month periods in previous years and the travel costs
from the port to the fishing grounds. Then a vessel chooses randomly from the
top 75 \% of fishing events as defined by the expected profit, that has a
seasonal component.

@@

\clearpage
\footnotesize
\input{F_changes.tex}

\input{Temp_proportions.tex}

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/pop_dist}
	\caption{Spatial density (log abundance) for each of the four
		populations at four time steps. The darker the colour the
		greater the density of the population. Note that you can see
		the diagonal isotropic patterns in populations 2 and 3 and
		concentrated spawning areas in the second row of the panels
		(t=18).}
	\label{fig:9}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/Combined_Movement}
	\caption{(A) The fishing locations (points) and movements (lines) of a
		single vessel during a trip overlaid on the revenue of a
		fishing site (catch x price); (B) the fishing locations of the
		vessel over several trips (value field changes over the period
		so not shown). Note that the field is wrapped on a torus so
		that distances between opposite side of the spatial domain are
		considered next to each other, hence apparent large movements;
		(C) the locations of multiple vessels from the same fleet
		overlaid on the value field, (D) the realised step distance and
		turning angles for a single vessel over the simulation.}
	\label{fig:mv}
\end{figure}

>>>>

To simulate fish population distribution in space and time a Gaussian spatial
process was employed to model habitat suitability for each of the populations
on a 2d grid.  We first defined a Gaussian random field process, $\{S(c) : c \in
\mathbb{R}^2\}$, where for any set of cells $c_{1}, \dots, c_{n}$, the joint
distribution of $S = \{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian with a
\textit{Matérn} covariance structure, where the correlation strength weakens
with distance. This enables us to model the spatial autocorrelation observed in
animal populations where density is more similar in nearby locations
\citep{Tobler1970, F.Dormann2007, Poos2007} and we change the parameters to
implement different spatial structures for the different populations using the
\textit{RandomFields} R package \citep{Schlater2015}. We define a stationary
habitat field with an anisotropic pattern (to simulate a depth gradient) and
combine it with a temporally dynamic thermal tolerance field to imitate two key
drivers of population dynamics. Each population was initialised at a single
location, and subsequently moved across the entire space according to a
probabilistic distribution based on habitat suitability (represented by the
normalised values from the GRFs), temperature and distance from current cell: 
\begin{equation}
	Pr(C_{wk+1} = J | C_{wk} =I) = \frac{\mathrm{e}^{-\lambda \cdot d_{I,J}} \cdot
		(Hab_{J,p}^2 \cdot
		Tol_{J,p,wk})}{\sum\limits_{c=1}^{C}\mathrm{e}^{-\lambda \cdot d} \cdot
		(Hab_{c,p}^2 \cdot Tol_{c,p,wk})}
\end{equation}
Where $d_{I,J}$ is the euclidean distance between cell $I$ and cell $J$,
$\lambda$ is a given rate of decay, $Hab_{c,p}^2$ is the squared index of
habitat suitability for cell $c$ and population $p$, with $Tol_{c,p,wk}$ the
temperature tolerance for cell $c$ by population $p$ in week $wk$ (see
below). \\

@@

Several studies \citep[for a review]{Girardin2016} have confirmed past activity
and past catch rates are strong predictors of fishing location choice. For this
reason, the fleet dynamics sub-model included a learning component, where a
vessel's initial fishing location in a trip was based on selecting from
previously successful fishing locations. This was achieved by calculating an
expected revenue based on the catches from locations fished in the preceding
trip as well as the same month periods in previous years and the travel costs
from the port to the fishing grounds. Then a vessel chooses randomly from the
top 70 \% of fishing events (defined as the `threshold') in terms of expected
profit within that season.

@@

\clearpage
\input{F_changes.tex}

\clearpage
\input{Temp_proportions.tex}

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/pop_dist}
	\caption{Spatial density (log abundance) for each of the four
		populations at four time steps. The darker the colour the
		greater the density of the population. Note that a diagonal
		anisotropic pattern representing a depth gradient can be
		clearly seen in populations 2 and 3. The concentrated spawning
		areas are also visible in the second row of the panels
		(t=18).}
	\label{fig:9}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/Combined_Movement}
	\caption{(A) The fishing locations (points) and movements (lines) of a
		single vessel during a trip overlaid on the revenue of a
		fishing site (landings x price); (B) the fishing locations of
		the vessel over several trips (value field changes over the
		period so not shown). Note that movements are a mixture of
		correlated random walk and experience-based, and that the field
		is wrapped on a torus so that distances between opposite side
		of the spatial domain are considered next to each other. For
		these reasons there are moves larger than the step length in D;
		(C) the locations of multiple vessels from the same fleet
		overlaid on the value field, (D) the realised step distance and
		turning angles for a single vessel over the simulation.}
	\label{fig:mv}
\end{figure}

### 2019-09-24 write_up/parameter_tables.tex
JJP updates

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population dynamics sub-module}
	\label{tab: pop_variable}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
		\hline
		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
		$\alpha_{d}$ & Proportion of annually recruited fish recruited
		during day $d$ & - \\
		\hline
		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
		\hline
		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
		$F_{c,d}$ & Instantaneous rate of fishing mortality in cell $c$
		on day $d$ & - \\
		$M_{c,d}$ & Instantaneous rate of natural mortality in cell $c$
		on day $d$ & - \\
		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
		\hhline{===}
		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
		$S_{c,d}$ & is the stock size in cell $c$ for day $d$ & $d^{-1}$ \\
		$\alpha$ & the maximum recruitment rate & kg  \\
		$\beta$ & the stock size required to produce half the maximum rate
		of recruitment & kg \\
		\bottomrule
		\end{tabular}
\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population movement sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population movement dynamics}} \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Habitat model}} \\
		\hline
		a & b & c \\
		\hline
		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
		\hline
		$T_{c,wk}$ & Temperature for cell in week & $^\circ$C \\
		$\mu_{p}$ & Mean of the thermal tolerance for population & $^\circ$C \\
		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
		the population & $^\circ$C \\
		\hline
		\multicolumn{3}{l}{\textit{Population movement model}} \\
		\hline
		$\lambda$ & decay rate for population movement & - \\
		$Hab^{2}_{c,p}$ & Square of habitat suitability for cell $c$ and
		population $p$ & - \\
		$Tol_{c,p,wk}$ & Thermal tolerance for population $p$ in cell
		$c$ at week $wk$ & - \\
		$d_{IJ}$ & euclidean distance between cell $I$ and cell $J$ & - \\
		\bottomrule
		\end{tabular}
	\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for fleet dynamics sub-module}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Short-term fleet dynamics}} \\
		\hhline{===}
		$Rev$ & Revenue from fishing tow & \euro \\
		$L_{p}$ & Landings of population $p$ & kg \\
		$Pr_{p}$ & Average price of population $p$ & \euro
		\hspace{0.1cm} kg$^{-1}$ \\
		StepL & Step length for vessel & euclidean distance \\
		Br & Bearing & degrees \\
		$k$ & Concentration parameter for Von mises distribution & - \\
		$\beta_{1}$ & shape parameter for step function & - \\
		$\beta_{2}$ & shape parameter for step function & - \\
		$\beta_{3}$ & shape parameter for step function & - \\
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}[!ht]
\caption{Population dynamics and movement parameter setting}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.015 & 1/0.05 & 1/0.01 & 1/0.005  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier & 10 & 10 & 10 & 10 \\
	Movement $\lambda$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit 'a' & 6 & 27 & 18 & 0.3  \\
	Beverton-Holt Recruit 'b' & 4 & 4 & 11 & 0.5 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.7 & 0.6 & 0.7 & 0.6 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	$wt$ & 1 & 1 & 1 & 1 \\
	$wt_{d-1}$ & 0.1 & 0.1 & 0.1 & 0.1 \\
	M (annual) & 0.2 & 0.1 & 0.2 & 0.1 \\
	\hline
	Movement dynamics & & & & \\
	\hline
	$\mu$ & 12 & 15 & 17 & 14 \\
	$\sigma^2$ & 8 & 9 & 7 & 10 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}

\begin{table}[!ht]
\caption{Fleet dynamics parameter setting}
\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
	\hline
	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
	\hline
	Targeting preferences & pop 2/4 & pop 1/3 & - & pop 4 & pop
	2/3 \\
	\hline
	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
	Price Pop3 & 350 & 350 & 350 & 350 & 350 \\
	Price Pop4 & 600 & 600 & 600 & 600 & 600 \\
	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
	$Q$ Pop2 & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
	$Q$ Pop4 & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
	\hline
	Exploitation dynamics &&&& \\
	\hline
	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
	step function $\beta_2$ & 10 & 15 & 8 & 12 & 7 \\
	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
	step function $rate$ & 20 & 30 & 25 & 35 & 20 \\
	Past Knowledge & T & T & T & T & T \\
	Past Year \& Month & T & T & T & T & T \\
	Past Trip & T & T & T & T & T \\
	Threshold & 0.7 & 0.7 & 0.7 & 0.7 & 0.7 \\
	Fuel Cost & 3 & 2 & 5 & 2 & 1 \\
	\hline
\end{tabular}
\label{tab:2}
\end{table}

>>>>

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population and recruitment
		dynamics sub-modules.}
	\label{tab: pop_variable}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
		\hline
		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
		$\alpha_{d}$ & Proportion of annually recruited fish recruited
		during day $d$ & - \\
		\hline
		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
		\hline
		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
		$F_{c,d}$ & Instantaneous rate of fishing mortality in cell $c$
		on day $d$ & - \\
		$M_{c,d}$ & Instantaneous rate of natural mortality in cell $c$
		on day $d$ & - \\
		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
		\hhline{===}
		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
		$B_{c,d}$ & biomass in cell $c$ for day $d$ & $d^{-1}$ \\
		$\alpha$ & the maximum recruitment rate (Beverton Holt)
		or maximum productivity per spawner (Ricker) & kg  \\
		$\beta$ & the stock size required to produce half the maximum rate
		of recruitment (Beverton Holt) or density dependent reduction
		in productivity per capita of SSB & kg \\
		\bottomrule
		\end{tabular}
\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population movement sub-module.}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
		\hline
		$T_{c,wk}$ & Temperature for cell in week & $^\circ$C \\
		$\mu_{p}$ & Mean of the thermal tolerance for population & $^\circ$C \\
		$\sigma^{2}_{p}$ & Standard deviation of thermal tolerance for
		the population & $^\circ$C \\
		\hline
		\multicolumn{3}{l}{\textit{Population movement model}} \\
		\hline
		$\lambda$ & Decay rate for population movement & - \\
		$Hab_{c,p}$ & Habitat suitability for cell $c$ and
		population $p$ & - \\
		$Tol_{c,wk,p}$ & Thermal tolerance for in cell $c$ at week $wk$
		for population $p$ & - \\
		$d_{I,J}$ & Euclidean distance between cell $I$ and cell $J$ & - \\
		\bottomrule
		\end{tabular}
	\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for fleet dynamics sub-module.}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		$Rev$ & Revenue from fishing tow & \euro \\
		$L_{p}$ & Landings of population $p$ & kg \\
		$Pr_{p}$ & Average price of population $p$ & \euro
		\hspace{0.1cm} kg$^{-1}$ \\
		Le & Step length for vessel & - \\
		Br & Bearing & degrees \\
		$k$ & Concentration parameter for von mises distribution & - \\
		$\beta_{1}$ & shape parameter for step function & - \\
		$\beta_{2}$ & shape parameter for step function & - \\
		$\beta_{3}$ & shape parameter for step function & - \\
		\bottomrule
	\end{tabular}
\end{table}

\begin{table}[!ht]
\caption{Population dynamics and movement parameter settings.}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.015 & 1/0.05 & 1/0.01 & 1/0.005  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier = 10 & & & & \\
	Movement $\lambda$ = 0.1 & & & & \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit $\alpha$ & 6 & 27 & 18 & 0.3  \\
	Beverton-Holt Recruit $\beta$ & 4 & 4 & 11 & 0.5 \\
	Beverton-Holt Recruit $\sigma^2$ & 0.7 & 0.6 & 0.7 & 0.6 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Spawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	$K$ = 0.3 & & & & \\
	$wt$ = 1 & & & & \\
	$wt_{d-1}$ = 0.1 & & & &  \\
	M (annual) & 0.2 & 0.1 & 0.2 & 0.1 \\
	\hline
	Movement dynamics & & & & \\
	\hline
	$\mu$ & 12 & 15 & 17 & 14 \\
	$\sigma^2$ & 8 & 9 & 7 & 10 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}

\begin{table}[!ht]
\caption{Fleet dynamics parameter setting.}
\begin{tabular}{ p{4cm } p{1.2cm} p{1.2cm} p{1.2cm} p{1.2cm} p{1.2cm}}
	\hline
	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
	\hline
	Targeting preferences & pop 2/4 & pop 1/3 & - & pop 4 & pop
	2/3 \\
	\hline
	Price $Pr_{p}1$ = 100 & & & & & \\
	Price $Pr_{p}2$ = 200 & & & & & \\
	Price $Pr_{p}3$ = 350 & & & & & \\
	Price $Pr_{p}4$ = 600 & & & & & \\
	$Q_{p}$ & 0.01 & 0.02 & 0.02 & 0.01 & 0.01 \\
	$Q_{p}$ & 0.02 & 0.01 & 0.02 & 0.01 & 0.03\\
	$Q_{p}$ & 0.01 & 0.02 & 0.02 & 0.01 & 0.02 \\
	$Q_{p}$ & 0.02 & 0.01 & 0.02 & 0.05 & 0.01 \\
	\hline
	Exploitation dynamics &&&& \\
	\hline
	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
	step function $\beta_2$ & 10 & 15 & 8 & 12 & 7 \\
	step function $\beta_3$ & Q90 & Q90 & Q85 & Q90 & Q80 \\
	step function $rate$ & 20 & 30 & 25 & 35 & 20 \\
	Past Knowledge = TRUE & & & & & \\
	Threshold & 0.7 & 0.7 & 0.7 & 0.7 & 0.7 \\
	Fuel Cost & 3 & 2 & 5 & 2 & 1 \\
	\hline
\end{tabular}
\label{tab:2}
\end{table}
